\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis

### 2018-04-03 paper/ms.tex
Christinas initial changes

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[twocolumn]{aastex62}
\usepackage{amsmath, amssymb, mathtools, bm}
\usepackage{cite}

\newcommand{\KTWO}{$\mathcal{K}\mathit{2}$}
\newcommand{\tess}{TESS}
\newcommand{\lightkurve}{\texttt{lightkurve}}
\newcommand{\LightCurve}{\texttt{LightCurve}}
\newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
\newcommand{\numpy}{\texttt{numpy}}

@@

\title{\lightkurve: a Python open source package for NASA's Kepler, K2, and TESS data analysis}

@@

    This paper presents an open source package for NASA's Kepler, \KTWO, and
    TESS.

@@

%% Keywords should appear after the \end{abstract} command.
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{editorials, notices ---
miscellaneous --- catalogs --- surveys}

\section{Introduction} \label{sec:intro}
NASA's Kepler, \KTWO, and \tess~missions have been delivering high-precision time
series data for a wide range of stellar types.
Cite Borucki et al for Kepler, Howell et al for K2, XXX for TESS.

While these missions have powerful pipelines which deliver high-precision
lightcurves for many objects (citation), analyses tailored for specific
science cases can often optimize the analysis.
For example:
1) a bigger aperture mask has been shown to yield additional planets in Kepler-XXX (cite Isabel),
2) custom tailored PSF photometry has been shown to disentangle the signals of stars in
dense clusters (cite Libralato et al),
3) the official pipelines tend to be optimized for signals at the duration of typical
planet transits (6 hours) and are not optimized for long-term trends such as those
seen in AGN (cite Krista Lynn Smith).

Explain PyKE exists and how it differs.
In this paper, we present a new Python package which makes the custom analysis
of target easy.  Based on AstroPy (cite Astropy).

Explain the structure of the paper and announce that we will show examples
of the 3 key features: manipulating lightcurves, creating lightcurves,
and removing systematics from lightcurves.

@@

In the same fashion, we can apply cotrending basis vector correction to
\KTWO lightcurves.

Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
the first nine coefficients for CBV correciton on \KTWO target
 \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
grid search curve can be set through model comparison heuristics like AIC, BIC,
or cross-validation \cite{ivezi2014}.

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[twocolumn]{aastex62}
\usepackage{amsmath, amssymb, mathtools, bm}

\newcommand{\ktwo}{{\it K$\mathit{2}$}}
\newcommand{\tess}{{\it TESS}}
\newcommand{\kepler}{{\it Kepler}}
\newcommand{\lightkurve}{\texttt{lightkurve}}
\newcommand{\LightCurve}{\texttt{LightCurve}} d
\newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
\newcommand{\numpy}{\texttt{numpy}}
\newcommand{\code}{\texttt}

@@

\title{\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis}

@@

  \begin{itemize}
  \item{We present \lightkurve, an open source package for analysis of flux time series using Python.}
  \item{\lightkurve is a general purpose tool.}
  \item{However, it is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions.}
  \end{itemize}

@@

\keywords{}

\section{Introduction} \label{sec:intro}

\paragraph{What is the background}
\begin{itemize}
\item{Time series photometry is available for a wide variety of astrophysical purposes and in a wide variety of formats.}
\item{This ranges from 30 year long time series of variable stars\cite{citationneeded} to short time-series of hours for X-Ray objects \cite{citationneeded}}
\item{In particular, NASA's \kepler and \ktwo missions have provided some of the most precise, long term monitoring of stars to date \cite{citationneeded}.}
\item{In the near future the \tess mission will delivering high-precision time series data for 90\% of the sky, providing light curves for X millions of object \cite{citationneeded}.}
\end{itemize}

\paragraph{What are we presenting}
\begin{itemize}
\item{We present \lightkurve as a general tool to use almost all time-series photometry, with a particular focus on \kepler, \ktwo~ and \tess.}
\item While these missions have powerful pipelines which deliver high-precision light curves for many objects (citation), \lightkurve allows bespoke analyses tailored for specific science cases.
\item These might include custom aperture photometry, PSF photometry in crowded field and studies of long period transient events such as supernovae and AGN.
\item{We have designed \lightkurve as a tool process this vast wealth of data easily and intuitively with many features and tools to remove reduce the overhead in using this data.}
\end{itemize}

\paragraph{How do you use lightkurve}
\begin{itemize}
\item designed to be flexible
\item nuts and bolts
\item open source
\item easy api
\end{itemize}

\paragraph{What is the selling point of lightkurve}
\begin{itemize}
\item There are two sides to the \lightkurve package. Firstly, \lightkurve can be used as an extraction package for creating time-series photometry from astronomical images such as \kepler Target Pixel Files (TPFs) or \tess Full Frame Images (FFIs). This includes simple aperture photometry, PSF photometry and centroiding.
\item Secondly, \lightkurve can be used for analysis of time-series photometry. This includes motion detrending, CBV corrections, outlier rejection and period folding.
\item Together these two sides can be combined to convert raw data from \kepler, \ktwo~ and \tess~ to cleaned light curves of exoplanet candidates, supernovae and extra-galactic objects.
\end{itemize}

\paragraph{What about pyke}
\begin{itemize}
\item previously there was pyke, don't spend too long on this
\item pyke is still available
\item \lightkurve uses only python
\item  new Python package which makes the custom analysis of target easy.  Based on AstroPy (cite Astropy).
\end{itemize}

\paragraph{Future resources?}
\begin{itemize}
\item This is \lightkurve 1.0
\item Anticipate adding new features
\end{itemize}

\paragraph{What's in this paper?}
\begin{itemize}
\item In this paper we discuss the basic components of \lightkurve
\item We will show three key components of analysis with \lightkurve; manipulating lightcurves, creating lightcurves,
and removing systematics from lightcurves.
\item \lightkurve has a full compliment of tutorials
\item More details can be found in our documentation at link.
\end{itemize}

@@

In the same fashion, we can apply cotrending basis vector correction to
\ktwo lightcurves.

Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
the first nine coefficients for CBV correciton on \ktwo target
 \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
grid search curve can be set through model comparison heuristics like AIC, BIC,
or cross-validation \cite{ivezi2014}.
